### 2016-05-11 README.Rmd
update README
Don’t evaluate the plotly commands
add travis and appveyor and badges

---
output:
  md_document:
    variant: markdown_github
always_allow_html: yes
---

@@

@@

Thanks to Carson Sievert, you can now add some really nifty interactivity into visdat by using `plotly::ggplotly`, allowing for information to be revealed upon mouseover of a cell. For example:

>>>>

---
output:
  md_document:
    variant: markdown_github
---

@@

<!-- add a TravisCI badge -->
[![Travis-CI Build Status](https://travis-ci.org/tierneyn/visdat.svg?branch=master)](https://travis-ci.org/tierneyn/visdat)

<!-- Add an appVeyor badge -->

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tierneyn/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/tierneyn/visdat)

@@

Thanks to Carson Sievert, you can now add some really nifty interactivity into visdat by using `plotly::ggplotly`, allowing for information to be revealed upon mouseover of a cell. The code to do this can be seen below, but is not shown as the github README doesn't support HTML interactive graphics...yet.
